Review of Assigned Readings

### 2017-12-29 paper/paper.tex
added outline for twitter part

		\itshape\textbf {Twitter}\\
		\textnormal {(Text for Twitter) Input Alen: Explain why twitter is the right source and and some facts about it}\\

>>>>

		\itshape\textbf {Twitter}\\
		\textnormal { Outline: Growth of Social Media, Opinion Mining, Twitter -> micro-blogging platform, tweets, functionalities, etc. ; Why good for measuring opinions ?  "gold mine"; Sentiment Analysis, What we do.
Comment Severin: This part will contain the following steps and will be mostly based on Stenqvist et al. Predicting Bitcoin price fluctuation
with Twitter sentiment analysis - sections 2.2, 2.3\newline
1) Introduction sentence -> growth of social media https://www.statista.com/statistics/278414/number-of-worldwide-social-network-users/\newline
2) Twitter as a "gold mine" to gather opinions -> What is twitter, Why is it valuable -> length of messages etc.\newline
3) Sentiment Analysis -> what is a sentiment analysis\newline
4) Sentiment Analysis of the term bitcoin based on twitter -> explain what we do }\\
